---
title: "G&S 3-11"
author: "Jiaheng Li"
date: "2021/2/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In order to meet our requirement, we need $\alpha$ enter the box from the bottom and exist from the top. Thus, these power curves also need to enter the box from the bottom. If a curve doesn't enter from the bottom, then the value of $\alpha(0.6)$ will be higher than 0.05 which the probablity of leading to a type I would be higher than 5 percent. Similarly, if a curve doesn't exist from the top, the value of $\alpha(0.8)$ will be lower than 0.95, then the probablity of type II error $1-\alpha(0.8)$ would be higher than 0.05.

We will be using the equation of $$\alpha=\sum_{k=m}^{n}{b(n,p,k)}$$ to calcluate the value of m for both of the situations.

(1) n=100, p=0.6 $\alpha=0.05$, then $$0.05=\sum_{k=m}^{n}{b(100,0.6,k)}$$ 

```{r}
biterm<-function(n,p,k){
  t=choose(n,k)*(p^k)*(1-p)^(n-k)
}
a=100
p1=0.6
n=100
term=biterm(n,p1,a)
while (term<0.05) {
 a=a-1
  term=term+biterm(n,p1,a)
}
print(a+1)
```
The smallest value of m is 69.

(2) n=100, p=0.8 $\alpha=0.95$, then $$0.95=\sum_{k=m}^{n}{b(100,0.8,k)}$$
```{r}
a=100
p2=0.8
n=100
term=biterm(n,p2,a)
while (term<0.95) {
  a=a-1
  term=term+biterm(n,p2,a)
}
print(a)
```
The largest value of m is 73.

Figure 3.7
```{r}
x<-seq(0.4,1,0.001)
alpha<-function(m,n,p){
  t=0
  for (i in m:n) {t=t+biterm(n,p,i)}
  return(t)
}
y <- alpha(69,100,x)
y1 <- alpha(73,100,x)
plot(x,y,col="gold",pch=16,cex=0.1,ylab="",main="Power Curve")
points(c(0.6,0.6,0.8,0.8),c(0.05,0.95,0.95,0.05),pch=19,cex=0.1)
lines(c(0.6,0.6,0.8,0.8,0.6),c(0.05,0.95,0.95,0.05,0.05),lty=2)
points(x,y1,col="deepskyblue",pch=16,cex=0.1)
lines(x,y1,col="deepskyblue",lty=1,cex=1)
lines(x,y,col="gold",lty=1,cex=1)
```

